Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-24 main.tex
indicação de tamanho na figura 3
indicação de quantidade de imagens na figura 3

To reduce the need for large annotated training sets by exploiting the user knowledge, we present a method, called \textcolor{red}{\emph{Feature Learning from Image Markers} (FLIM)}, that needs a minimal set of images to learn the filters of each convolutional layer. The user selects the number of convolutional layers, their filter sizes, \textcolor{red}{a few images from a training set}, and draws markers in image regions that best discriminate the classes. \textcolor{red}{By clustering patches extracted from marker pixels at the input of each convolutional layer, FLIM finds filters that enhance those regions at the convolutional layers' output. The remaining training images can then be used to train the fully connected layers or another classifier.} The CNN architecture could also be optimized based on visual analytics~\cite{SpinnerTVCG2020}, but we have not explored this option yet. \textcolor{red}{In interactive semantic segmentation, user-selected clicks can affect part of the network to improve segmentation, but the filters are not designed from those markers~\cite{SofiiukCVPR2020}.}

@@

     %images----------------------------
    \node (mimg1) [image, above right=-2em and 2.8em of put] {\includegraphics[width=.08\textwidth]{figures/markers1.png}};
    \node (mimg2) [image, below left=-5em of mimg1] {\includegraphics[width=.08\textwidth]{figures/markers2.png}};
    \node (mimg3) [image, below left=-5em of mimg2] {\includegraphics[width=.08\textwidth]{figures/markers3.png}};
    \node (mimg4) [image, below left=-5em of mimg3] {\includegraphics[width=.08\textwidth]{figures/markers4.png}};

@@

     %\draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
%(img3.west) -- (img1.north) node [black,midway,xshift=0.8cm, label = {[label distance = 0.1em]above:{Images}}] {};

>>>>

To reduce the need for large annotated training sets by exploiting the user knowledge, we present a method, called \textcolor{red}{\emph{Feature Learning from Image Markers} (FLIM)}, that needs a minimal set of images to learn the filters of each convolutional layer. The user selects the number of convolutional layers, their filter sizes, \textcolor{red}{a few images from a training set}, and draws markers in image regions that best discriminate the classes. \textcolor{blue}{The user takes a couple of minutes to select images and draw markers in those images}. \textcolor{red}{By clustering patches extracted from marker pixels at the input of each convolutional layer, FLIM finds filters that enhance those regions at the convolutional layers' output. The remaining training images can then be used to train the fully connected layers or another classifier.} The CNN architecture could also be optimized based on visual analytics~\cite{SpinnerTVCG2020}, but we have not explored this option yet. \textcolor{red}{In interactive semantic segmentation, user-selected clicks can affect part of the network to improve segmentation, but the filters are not designed from those markers~\cite{SofiiukCVPR2020}.}

@@

     %images----------------------------
    \node (mimg1) [image, above right=-2.5em and 2.8em of put] {\includegraphics[width=.08\textwidth]{figures/markers1.png}};
    \node (mimg2) [image, below left=-5em of mimg1] {\includegraphics[width=.08\textwidth]{figures/markers2.png}};
    \node (mimg3) [image, below left=-5em of mimg2] {\includegraphics[width=.08\textwidth]{figures/markers3.png}};
    \node (mimg4) [image, below left=-5em of mimg3] {\includegraphics[width=.08\textwidth]{figures/markers4.png}};

@@

     \draw [decorate,decoration={brace,amplitude=4pt,raise=5pt}]
(img3.north west) -- (img1.north west) node [black,midway,xshift=-0.4cm, yshift=0.4cm, rotate=45] {\small 200};

\draw [decorate,decoration={brace,amplitude=4pt,raise=5pt}]
(simg4.north west) -- (simg1.north west) node [black,midway,xshift=-0.4cm, yshift=0.4cm, rotate=45] {\small 4};

\draw [decorate,decoration={brace,amplitude=4pt,raise=5pt}]
(mimg4.north west) -- (mimg1.north west) node [black,midway,xshift=-0.4cm, yshift=0.4cm, rotate=45] {\small 4};
